### 2018-08-30 ms.tex
Small additions to data methods.

We used two data sources that reflect malaria burden; point prevalence surveys and polygon-level, aggregated incidence data.
We selected Madagascar and Indonesia as case examples as they have both good surveillance data and good country wide surveys from approximately the same time.
Given the available data we chose to focus our analysis on 2012-2015 for Indonesia and 2013-2014 for Madagascar.

@@

The prevalence survey data were extracted from the MAP prevalence survey database \cite{bhatt2015effect}.
As the prevalence surveys cover different age ranges they were standardised using the model from \cite{smith2007standardizing}.

@@

>>>>

We used two data sources that reflect malaria burden; point prevalence surveys and polygon-level, aggregated incidence data.
We selected Madagascar, Senegal and Indonesia as case examples as they all have good surveillance data and good country wide surveys from approximately the same time.
Given the available data we chose to focus our analysis on 2012-2015 for Indonesia and 2013-2014 for Madagascar.

@@

The prevalence survey data were extracted from the Malaria Atlas Project prevalence survey database \cite{bhatt2015effect}.
As the prevalence surveys cover different age ranges they were standardised using the model from \cite{smith2007standardizing}.

@@

The polygon level surveillance data were collated from various government reports.
To account for underreporting of clinical cases due to lack of treatment seeking, missed case reports and cases that sought medical attention outside the public health systems, the methods in \cite{cibulskis2011worldwide} were used.
Where species specific reports were given, these were used. 
When reports were no species specific, national estimates of the ratio between \emph{P. falciparum} and \emph{P. vivax} cases were used to calculate \emph{P. falciparum} only cases.
